Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
sampled at 44100 Hz

%For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. Larger datasets exists: the
%Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge.%
The experiments in this paper are carried out on the DCASE 2013 \cite{7100934} and DCASE 2016 \cite{Mesaros2016_EUSIPCO} datasets.
The DCASE 2013 dataset consists of two parts, namely a public and a private subset, each made up of $100$ $30$-second recordings of various acoustic scenes. The $100$ recordings are evenly divided into $10$ acoustic scene classes. To build the DCASE 2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE 2013 dataset enjoys an interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.
In addition, it is still a challenging dataset, with a state-of-the-art system based using handcrafted features as input to SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieve between $84\%$ and $87\%$ on DCASE 2013 depending on the prior knowledge used during training \cite{phan2016label}.

>>>>

%For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. Larger datasets exists: the
%Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge.%
The experiments in this paper are carried out on the DCASE 2013 \cite{7100934} and DCASE 2016 \cite{Mesaros2016_EUSIPCO} datasets.
The DCASE 2013 dataset consists of two parts, namely a public and a private subset, each made up of $100$ $30$-second recordings of various acoustic scenes, sampled at $44100\,\mathrm{Hz}$. The $100$ recordings are evenly divided into $10$ acoustic scene classes. To build the DCASE 2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE 2013 dataset enjoys an interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.
In addition, it is still a challenging dataset, with a state-of-the-art system based using handcrafted features as input to SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieve between $84\%$ and $87\%$ on DCASE 2013 depending on the prior knowledge used during training \cite{phan2016label}.
